Figures to insert in text

### 2018-04-13 Chapters/Chapter02.tex
INTRO: 1.3 seemingly complete.  1.2 and 1.1 remaining

Suddenly, you feel the danger.  You tighten your grip on the child's hand and step up your walking.  In these large cities, walking on a dark alley was never recommended, but somehow that's what you did, and now everthing you think of is to get out to safety.  You are afraid of something, but you cannot explain --- in rigorous detail, at least --- what exatcly is causing your fear. One just feels it. We may interpret this situation as clues of the present --- a dark alley; a giant metropolitan area; people going on about their lives mostly indifferent from each other; constrained routes ahead and behind you; a general lack of activity; that very feeling that something isn't right... without knowing precisely what isn't right, or even what `right' means... etc. --- recalling past experiences from memory and thus generating the feeling. Our memory is able to make a parallel between previous experiences and the clues. Although one has never been in the exactly same situation, one's brain involuntarily makes an analogy and recognizes the possibility of danger. The whole process happens so fast it feels like it only took a single unit of psychological time.

@@

Sparse Distributed Memory (SDM) \citep{Kanerva1988} is a mathematical model of long-term memory that has a number of neuroscientific and psychologically plausible dynamics. This model may be applied in all sort of applications because of its incredible ability to closely reflect the human capacity to remember past experiences from clues of the present.

@@

SDM has been applied in many different fields, like pattern recognition \citep{norman2003modeling, rao1995natural}, noise reduction \citep{Meng2009}, handwriting recognition \citep{fan1997genetic}, robot automation \citep{Rajesh1998, mendes2008robot}, and so forth. \citet{Linhares2011} has shown that SDM respects the limits of short-term memory discussed by \citet{Miller1955} and \citet{Cowan2001}. Despite all those applications, there is not a reference implementation which would allow one to replicate the results published in a paper, to check the source code for details, and to improve it. Thus, even though intriguing results have been achieved using SDM, it requires counter-productive, duplicate effort from researchers to build on top of previous work.

@@

\begin{enumerate}
    \item The original hardware implementation developed by NASA [4];

    \item LISP implementation for the Connection Machine [60];

    \item APL implementation [59];

    \item FPGA implementation \citep{silva_reconfigurable_2004};

    \item C Binary Vector Symbols (CBVS): includes SDM implementation in C as a part of vector symbolic architecture[54] developed by EISLAB at Luleå University of Technology: http://pendicular.net/cbvs.php[55];

    \item CommonSense ToolKit (CSTK) for realtime sensor data processing developed at the Lancaster University includes implementation of SDM in C++: http://cstk.sourceforge.net/[56];

    \item Learning Intelligent Distribution Agent (LIDA) developed by Stan Franklin's lab at the University of Memphis includes implementation of SDM in Java. \footnote{http://ccrg.cs.memphis.edu/framework.html};

@@

Let us analyse these.  The Connection Machine is obsolete.  The NASA implementation is hardware-based and obsolete.  APL, while influential, is not a mainstream language in science.

The FPGA implementation by \citet{silva_reconfigurable_2004} has yielded a fast scan of hard locations, provided one has access to the proper hardware. Their article claims a four-fold speedup over assembly language; but it does not deal with parallel processing details.  For example, it is unclear whether there was more than a single thread running on the software implementation.  Note that the framework presented here is also able to reconfigure field-programmable gate arrays, through the OpenCL heterogeneous computing platform ability to interface with Hardware Description Language and hence, reconfigure FPGAs \citep{waidyasooriya2018design, czajkowski_opencl_2012} for our tasks.

@@

Note that all these criticisms apply to the implementations in both the `common sense toolkit' and the `C Binary Vector Symbols' REF.  While these implementations have around 150 lines of C++; at last count, the \emph{documentation of our implementation} had over 100 \emph{pages}. We aim a higher here, and, to us, SDM is at center stage.

>>>>

Suddenly, you feel the danger.  You tighten your grip on the child's hand and step up your walking.  In these large cities, walking on a dark alley was never recommended, but somehow that's what you did, and now everthing you think of is to get out to safety.  You are afraid of something, but you cannot explain --- in rigorous detail, at least --- what exactly is causing your fear. One just feels it. We may interpret this situation as clues of the present --- a dark alley; a giant metropolitan area; people going on about their lives mostly indifferent from each other; constrained routes ahead and behind you; a general lack of activity; that very feeling that something isn't right... without knowing precisely what isn't right, or even what `right' means... etc. --- recalling past experiences from memory and thus generating the feeling. Our memory is able to make a parallel between previous experiences and the clues. Although one has never been in the exactly same situation, one's brain involuntarily makes an analogy and recognizes the possibility of danger. The whole process happens so fast it feels like it only took a single unit of psychological time.

@@

Sparse Distributed Memory (SDM) \citep{Kanerva1988} (see also \citep{kanerva_sparse_1993, denning_sparse_1989} is a mathematical model of long-term memory that has a number of neuroscientific and psychologically plausible dynamics. This model may be applied in all sort of applications because of its incredible ability to closely reflect the human capacity to remember past experiences from the subtlest of clues.

@@

As expected for such an important thery, SDM has been applied in many different fields, like pattern recognition \citep{norman2003modeling, rao1995natural}, noise reduction \citep{Meng2009}, handwriting recognition \citep{fan1997genetic}, robot automation \citep{Rajesh1998, mendes2008robot}, and so forth. \citet{Linhares2011} has shown that SDM respects the limits of short-term memory discussed by \citet{Miller1955} and \citet{Cowan2001}. Despite this, there is not a reference implementation which would allow one to replicate the results published in a paper, to check the source code for details, and to improve it. Thus, even though intriguing results have been achieved using SDM, it requires counter-productive, duplicate effort from researchers to build on top of previous work.

@@

\begin{enumerate}
    \item The original 1989 hardware implementation developed in NASA by \citet{flynn_sparse_1989};

    \item a 1995 LISP implementation for the Connection Machine by \citet{turk_kanervas_1995};

    \item a 1992 APL implementation by \citet{surkan_wsdm:_1992};

    \item a 2004 FPGA implementation by \citet{silva_reconfigurable_2004};

    \item a 2005 C++ implementation by \citet{berchtold_processing_2005} from Lancaster University, in the `CommonSense ToolKit' (CSTK) \citep{noauthor_cstk:_nodate} for realtime sensor data includes SDM as one of its classification algorithms;

    \item  a 2015 `C Binary Vector Symbols (CBVS)':  includes SDM implementation as a part of  vector symbolic architecture developed by \citet{emruli_vector_2015} from EISLAB at Luleå University of Technology \footnote{The code is available at http://pendicular.net/cbvs.php};

    \item a 2013 Java implementation `Learning Intelligent Distribution Agent' (LIDA) developed by \citep{franklin_lida:_2014, snaider_integer_2013, snaider_modular_2014} Stan Franklin from the University of Memphis includes implementation. \footnote{http://ccrg.cs.memphis.edu/framework.html};

@@

Let us analyze these.  The Connection Machine is obsolete.  The NASA implementation is hardware-based and obsolete.  APL, while reasonably influential, is not a mainstream language in science.

The FPGA implementation by \citet{silva_reconfigurable_2004} has yielded a fast scan of hard locations at low energy costs, provided one has access to the proper hardware. Their article claims a four-fold speedup over assembly language; but it does not deal with parallel processing details.  For example, it is unclear whether there was more than a single thread running on the software implementation.  Note that the framework presented here is also able to reconfigure field-programmable gate arrays, through the OpenCL heterogeneous computing platform ability to interface with Hardware Description Language and hence, reconfigure FPGAs \citep{waidyasooriya2018design, czajkowski_opencl_2012} for our tasks.

@@

Note that all these criticisms apply to the implementations in both the `common sense toolkit' and the `C Binary Vector Symbols' \citep{berchtold_processing_2005, noauthor_cstk:_nodate, emruli_vector_2015}.  While these implementations have around 150 lines of C++; at last count, the \emph{documentation of our implementation} had \emph{over 100 pages} \citep{linhares_sparse_2018}: they have aimed at running code, and we aim at improving a community and industry standard.
